\LARGE \bf Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions

### 2021-08-30 Papers/Stochastic_Uncertainty_Propagation_TPS/JKO_Power_Systems_TPS.tex
updates

\begin{figure*}[ht!]
   \subfigure[]{\includegraphics[width=0.322\textwidth]{Case0_OmegaMarginals.png}}
   \hspace{\fill}
   \subfigure[]{\includegraphics[width=0.322\textwidth]{Case1_OmegaMarginals.png}}
   \hspace{\fill}
   \subfigure[]{\includegraphics[width=0.309\textwidth]{Case0Case1Combined_Gen4_OmegaMarginals.png}}
\caption{\small{For $i=1,\hdots,5$, the $\omega_{i}$ marginals (a) for Case I, and (b) for Case II, resulting from the IEEE 14 bus simulation described in Sec. \ref{subsec:NumSimIEEEBus}. (c) Comparison of the $\omega_{4}$ marginals for bus 6 in the nominal (Case I) and post-fault (Case II) scenarios.}}
\vspace*{-0.1in}
\label{fig:IEEE14omegamarginalsCase12}
\end{figure*}

@@

With step size $h=10^{-3}$, we discretized time $t\in[0,1]$. Using the algorithm detailed in Sec. \ref{sec:ProxAlgo}, for all the three cases, we propagated $N=1000$ random samples from \eqref{rho0IEEE14}, and evaluated at \eqref{rho0IEEE14}, to update the scattered weighted point clouds $\{\bm{x}_{k}^{i},\varrho_{k}^{i}\}_{i=1}^{N}$ over $\mathbb{T}^{5}\times\mathbb{R}^{5}$ at times $t_{k}:=kh$, $k\in\mathbb{N}$. In Algorithm \ref{algo:KineticProx}, we used the algorithmic parameters $\varepsilon=0.05$, $\delta=10^{-3}$, $\ell_{\max}=300$.

@@

Fig. \ref{fig:IEEE14omegamarginalsCase12} shows the corresponding univariate $\omega_{i}$-marginal PDFs. In particular, Fig. \ref{fig:IEEE14omegamarginalsCase12}(c) helps compare the $\omega_{4}$ marginal evolution for bus 6 in the nominal (Case I) and post-fault (Case II) scenarios. Since Case II considers the failure of line 13, from Fig. \ref{fig:Motivating} we intuitively expect that the transient effects of this fault will be prominent for bus 6 (generator 4). Indeed, Fig. \ref{fig:IEEE14omegamarginalsCase12}(c) shows that although the $\omega_{4}$ marginals in both Case I and II, at all times have highest probability around $0$ rad/s, the post-fault marginals show larger spread or dispersion of the probability mass, as expected. That the generator 4 states in Case II have larger uncertainties than in Case I, is also visible in the bivariate marginal plots if we compare the fourth row in Fig. \ref{fig:IEEE14marginalsCase0} with the same in Fig. \ref{fig:IEEE14marginalsCase1}.

Fig. \ref{fig:CompTimeIEEE14bus} shows the computational times needed to update $\{\bm{x}_{k}^{i},\varrho_{k}^{i}\}_{i=1}^{N}$ via the algorithm in Sec. \ref{sec:ProxAlgo}, for both Cases I and II.

\begin{table}[t]
\centering
\begin{tabular}{| l | l |} 
\hline
Parameter description & Values\\
\hline\hline
&\\
nominal frequency & $f_{0} = 60$ Hz\\
&\\
inertia & $m_{i}\in{\rm{Unif}}\left([2,12]\right)/2\pi f_{0}$\\
& \\
damping coefficient & $\gamma_{i}\in{\rm{Unif}}\left([20,30]\right)/2\pi f_{0}$\\
& \\
diffusion coefficient & $\sigma_{i}\in{\rm{Unif}}\left([1,5]\right)$\\
& \\
tangent of phase shift & $\tan\varphi_{ij}\begin{cases}
=0 & \text{for}\; i=j\\
\in{\rm{Unif}}\left([0,0.25]\right)& \text{for}\; i\neq j
\end{cases}$\\
& \\
effective power input & $P_{i}\in{\rm{Unif}}\left([0,10]\right)$\\
& \\
coupling coefficient & $k_{ij}\begin{cases}
=0 & \text{for}\; i=j\\
\in{\rm{Unif}}\left([0.7,1.2]\right) & \text{for}\; i\neq j	
\end{cases}$\\
& \\
\hline
\end{tabular}
\vspace*{0.1in}
\caption{Parameters used for the numerical simulation in Sec. \ref{subsec:NumSimSynthetic}. The indices $i,j\in\{1,\hdots,n\}$ where the number of generators $n=50$ in Sec. \ref{subsec:NumSimSynthetic}.}
\label{table:ParamUncertaintiesSynthetic}
\vspace*{-0.35in}
\end{table}

>>>>

\begin{figure*}[ht!]
   \subfigure[]{\includegraphics[width=0.322\textwidth]{Case0_OmegaMarginals.png}}
   \hspace{\fill}
   \subfigure[]{\includegraphics[width=0.322\textwidth]{Case1_OmegaMarginals.png}}
   \hspace{\fill}
   \subfigure[]{\includegraphics[width=0.309\textwidth]{Case0Case1Combined_Gen4_OmegaMarginals.png}}
\caption{\small{For $i=1,\hdots,5$, the $\omega_{i}$ marginals (a) for \textbf{Case I}, and (b) for \textbf{Case II}, resulting from the IEEE 14 bus simulation described in Sec. \ref{subsec:NumSimIEEEBus}. (c) Comparison of the $\omega_{4}$ marginals for bus 6 in the nominal (\textbf{Case I}) and post-fault (\textbf{Case II}) scenarios.}}
\vspace*{-0.1in}
\label{fig:IEEE14omegamarginalsCase12}
\end{figure*}

@@

With step size $h=10^{-3}$, we discretized time $t\in[0,1]$. Using the algorithm detailed in Sec. \ref{sec:ProxAlgo}, for both cases, we propagated $N=1000$ random samples from \eqref{rho0IEEE14}, and evaluated at \eqref{rho0IEEE14}, to update the scattered weighted point clouds $\{\bm{x}_{k}^{i},\varrho_{k}^{i}\}_{i=1}^{N}$ over $\mathbb{T}^{5}\times\mathbb{R}^{5}$ at times $t_{k}:=kh$, $k\in\mathbb{N}$. In Algorithm \ref{algo:KineticProx}, we used the algorithmic parameters $\varepsilon=0.05$, $\delta=10^{-3}$, $\ell_{\max}=300$.

@@

Fig. \ref{fig:IEEE14omegamarginalsCase12} shows the corresponding univariate $\omega_{i}$-marginal PDFs. In particular, Fig. \ref{fig:IEEE14omegamarginalsCase12}(c) helps compare the $\omega_{4}$ marginal evolution for bus 6 in the nominal (\textbf{Case I}) and post-fault (\textbf{Case II}) scenarios. Since \textbf{Case II} considers the failure of line 13, from Fig. \ref{fig:Motivating} we intuitively expect that the transient effects of this fault will be prominent for bus 6 (generator 4). Indeed, Fig. \ref{fig:IEEE14omegamarginalsCase12}(c) shows that although the $\omega_{4}$ marginals in both \textbf{Case I} and \textbf{II}, at all times have highest probability around $0$ rad/s, the post-fault marginals show larger spread or dispersion of the probability mass, as expected. That the generator 4 states in \textbf{Case II} have larger uncertainties than in \textbf{Case I}, is also visible in the bivariate marginal plots if we compare the fourth row in Fig. \ref{fig:IEEE14marginalsCase0} with the same in Fig. \ref{fig:IEEE14marginalsCase1}.

Fig. \ref{fig:CompTimeIEEE14bus} shows the computational times needed to update $\{\bm{x}_{k}^{i},\varrho_{k}^{i}\}_{i=1}^{N}$ via the algorithm in Sec. \ref{sec:ProxAlgo}, for both \textbf{Cases I} and \textbf{II}.

\begin{table}[t]
\centering
\begin{tabular}{| l | l |} 
\hline
Parameter description & Values\\
\hline\hline
&\\
nominal frequency & $f_{0} = 60$ Hz\\
&\\
inertia & $m_{i}\in{\rm{Unif}}\left([2,12]\right)/2\pi f_{0}$\\
& \\
damping coefficient & $\gamma_{i}\in{\rm{Unif}}\left([20,30]\right)/2\pi f_{0}$\\
& \\
diffusion coefficient & $\sigma_{i}\in{\rm{Unif}}\left([1,5]\right)$\\
& \\
tangent of phase shift & $\tan\varphi_{ij}\begin{cases}
=0 & \text{for}\; i=j\\
\in{\rm{Unif}}\left([0,0.25]\right)& \text{for}\; i\neq j
\end{cases}$\\
& \\
effective power input & $P_{i}\in{\rm{Unif}}\left([0,10]\right)$\\
& \\
coupling coefficient & $k_{ij}\begin{cases}
=0 & \text{for}\; i=j\\
\in{\rm{Unif}}\left([0.7,1.2]\right) & \text{for}\; i\neq j	
\end{cases}$\\
& \\
\hline
\end{tabular}
\vspace*{0.05in}
\caption{Parameters used for the numerical simulation in Sec. \ref{subsec:NumSimSynthetic}. The indices $i,j\in\{1,\hdots,n\}$ where the number of generators $n=50$ in Sec. \ref{subsec:NumSimSynthetic}.}
\label{table:ParamUncertaintiesSynthetic}
\vspace*{-0.35in}
\end{table}

### 2021-08-30 Papers/Stochastic_Uncertainty_Propagation_TPS/JKO_Power_Systems_TPS_10pg.tex
updates

\begin{figure*}[t]
\centering
\includegraphics[width=0.8\linewidth]{IEEE14BivariateMarginalComparison.pdf}
\caption{\small{Comparison of the $(\theta_{4},\omega_{4})$ marginals for bus 6 in the nominal (Case I) and post-fault (Case II) scenarios in the IEEE 14 bus simulation described in Sec. \ref{subsec:NumSimIEEEBus}.}}
\vspace*{-0.2in}
\label{fig:IEEE14marginalsBivariateComparison}
\end{figure*}

@@

\begin{figure}[ht!]
\includegraphics[width=0.85\linewidth]{Case0Case1Combined_Gen4_OmegaMarginals.png}
\caption{\small{Comparison of the $\omega_{4}$ marginals for bus 6 in the nominal (Case I) and post-fault (Case II) scenarios in the IEEE 14 bus simulation described in Sec. \ref{subsec:NumSimIEEEBus}.}}
\vspace*{-0.1in}
\label{fig:IEEE14omegamarginalsCase12}
\end{figure}

@@

Fig. \ref{fig:CompTimeIEEE14bus} shows the computational times for updating $\{\bm{x}_{k}^{i},\varrho_{k}^{i}\}_{i=1}^{N}$ via the algorithm in Sec. \ref{sec:ProxAlgo} for Cases I and II.

>>>>

\begin{figure*}[t]
\centering
\includegraphics[width=0.8\linewidth]{IEEE14BivariateMarginalComparison.pdf}
\caption{\small{Comparison of the $(\theta_{4},\omega_{4})$ marginals for bus 6 in the nominal (\textbf{Case I}) and post-fault (\textbf{Case II}) scenarios in the IEEE 14 bus simulation described in Sec. \ref{subsec:NumSimIEEEBus}.}}
\vspace*{-0.2in}
\label{fig:IEEE14marginalsBivariateComparison}
\end{figure*}

@@

\begin{figure}[ht!]
\includegraphics[width=0.85\linewidth]{Case0Case1Combined_Gen4_OmegaMarginals.png}
\caption{\small{Comparison of the $\omega_{4}$ marginals for bus 6 in the nominal (\textbf{Case I}) and post-fault (\textbf{Case II}) scenarios in the IEEE 14 bus simulation described in Sec. \ref{subsec:NumSimIEEEBus}.}}
\vspace*{-0.1in}
\label{fig:IEEE14omegamarginalsCase12}
\end{figure}

@@

Fig. \ref{fig:CompTimeIEEE14bus} shows the computational times for updating $\{\bm{x}_{k}^{i},\varrho_{k}^{i}\}_{i=1}^{N}$ via the algorithm in Sec. \ref{sec:ProxAlgo} for \textbf{Cases I} and \textbf{II}.
